\chapter{Introduction}

\textit{Write this chapter LAST.  Should be 5 to 10 pages.  This chapter provides a quick summary of the essential contents of the research project, principal results and contents of the report.  The target audience is members of the jury who do NOT have time to completely read all 21 reports, as well academic members of other juries who wish to compare this work to other works. }

\section{Background}
\textit{This is a generic title. Replace it with an actual title that describes the context of the work.\\
Short $1/2$ page summary of the technological context of the work and why it is interesting or important}\\
\\
\\
\begin{itemize}
	\item 	Osteoporosis study
	\item 	Need to study nano scale bone structure
	\item 	Nano CT scan in ESRF
\end{itemize}



\section{Problem Statement}
\textit{This is a generic title. Replace it with an actual title that describes the context of the work.\\
Approx ½ to 1 page description of the research problems that was addressed and what was required to address it. }\\
\\
\\
\begin{itemize}
	\item 	High radiation dose $->$ changing sample composition, sample motion...
	\item 	Need to use compress sensing for low dose reconstruction, not so much done in nano scale and on biological samples
\end{itemize}

\section{Scientific Approach and Investigative Method and Results}
\textit{This is a generic title. Replace it with an actual title that describes the context of the work.\\
Approx  1 to 2  page description of the scientific approach or approaches to a solution and how it was   investigated and evaluated.  Present a summary of the principal results obtained.} \\
\\
\\
\begin{itemize}
	\item 	Use of iterative reconstruction methods, presentation of SB-TV-2D, SB-TV-3D
	\item 	Evaluation : metrics description (metrics proposed in 2nd meeting) (mean squared error, psnr, SIFT detection? All in 3D, 2D (xy, yz, xz))
	\item 	Description of main results
\end{itemize}

\section{Contents of this report}

\textit{Approx ½ page per chapter.  Summarize the contents of the subsections of each chapter. Give the topics addressed and summarize what is written in each chapter.}
