\chapter{Practical implementation }
\textit{This is a generic title. Replace it with an actual title that describes the context of the work.\\
Give a concrete discussion of how the proposed solution was (or could be) implemented or evaluated.}\\
\\
\\

explain method to validate low dose / LD protocol / Acquisition
\section{Compressed Sensing Formulation}

$$
\min_u ||Wu||_1 st Fu = f
$$
3 conditions: $u$ sparce, Wu ..., incoherence.\\
$u$ sparce in domain $W$\\
CS in $||Wu||_p$ with $p\leq 1$ -> Bone details, $p\leq 1$ preserves borders.\\
TV non differentiable: $(TV)' = \frac{1}{\nabla u}$

\section{Split Bregman iterative reconstruction}
We propose to use iterative reconstruction with the algorithm described by \cite{goldstein2009split}. Split Bregman algorithm gives a solution to an L1 constrained problem. We will here describe the bregman iteration and it's application to L2 minimisation reconstructions which will be used in our algorithm.
    \subsection{Split Bregman iteration}
    Using Split Bregman we wish to solve the constrained reconstruction optimization problem described in the section \ref{} and set $W = \nabla$ as it has been shown to be efficient:
    \begin{equation}
        \min\limits_{u}||\nabla u||_1 \mbox{ such that } Fu=f
        \label{Eq:ConstPblm}
    \end{equation}
 Such constrained problem problems are difficult to solve directly. For this reason we need to define a new unconstrained problem. Luckily it is possible to approximate (\ref{Eq:ConstPblm}) as:
    \begin{equation}
        \min_{u}||\nabla u||_1 + \frac{\lambda}{2}||Fu-f||_2^2
    \end{equation}
    
    The Bregman iteration allows us to reduce \ref{Eq:ConstPblm} in even shorter unconstrained problems using Bregman distances. These constrained problem can be resolved iteratively as follows:
    \begin{equation}
        \begin{aligned}
            u^{k+1} &= \min_{u} ||\nabla u||_1 + \frac{\lambda}{2}||Fu - f^k||_2^2 \\
           f^{k+1} &= f^k + f - Fu^k
        \end{aligned}
    \end{equation}
    \subsection{L1 regularization problem}
    Our compressed sensing reconstruction method is based on L1 regulation and gradient. It is hence difficult to minimize. A splitting technique must be formulated and we will see how to solve it iteratively with split Bregman.\\
    The idea is to "de-couple" the L1 and L2 parts of our original problem. We wish to minimize the Total Variation $\nabla u$ of the image and a weight function $H()$. Splitting can be done by introducing new variable and define a new constraint:
    \begin{equation}
        \label{Eq:L1Const}
        \min_{u,d}||d||_1 + H(u) \mbox{ such that } d = \nabla u
    \end{equation}
    Using Bregman on it again we get other problems that can be splitted:%Which can be computed iteratively using Split Bregman iteration as:
    \begin{equation}
        \begin{aligned}
            (u^{k+1},d^{k+1}) &= \min_{u,d} ||d||_1 + H(u) +     \frac{\lambda}{2}||d - \nabla u - b^k||^2_2\\
            b^{k+1} &= b^k + \nabla_{u^{k+1}} - d^{k+1}
    \end{aligned}
    \end{equation}
\section{SB-TV-2D reconstruction}
    isotropic TV denoising pbl: 
    \begin{equation}
        \min_{u} ||\nabla u||_1 \mbox{ such that } ||Fu - f||_2^2 < \sigma^2
    \end{equation}
    
    where $\nabla u = (\nabla_x,\nabla_y)u$, $f$ represents the projection space, $F$ the projection operator, $u$ the image domain and $\sigma$ represents the variance of the signal noise.
    \begin{equation}
        \begin{aligned}
            u^{k+1} &= \min_{u}||\nabla u||_1 + \ \frac{\lambda}{2}||Fu - f^k||_2^2\\
            f^{k+1} &= f^k + f - F_u^k
        \end{aligned}
    \end{equation}

	We fall here into an unconstrained problem which is not steight forwardly solved. In order to get a constrained problem we will insert a variable d such that $d = \nabla u$.\\
	We can now use the Split Bregman iteration in order to solve our new problem: 
     \begin{equation}
        \begin{aligned}
            u^{k+1} &= \min_{u,d}||d||_1 + \ \frac{\lambda}{2}||Fu - f^k||_2^2 \mbox{ such that } d = \nabla u\\
            f^{k+1} &= f^k + f - F_u^k
        \end{aligned}
    \end{equation}
	And get to a solution where L1 and L2 elements of our original problem are spleted into two equations:
    \begin{equation}
        \begin{aligned}
            u^{k+1} &= \min_{u} \frac{\mu}{2}||Fu - f^k||_2^2 + \frac{\lambda}{2} ||d^k - \nabla u - b^k||_2^2\\
            d^{k+1} &= \min_{u} ||d||_1 + \frac{\lambda}{2}||d - \nabla u-b^k||_2^2\\
            b^{k+1} &= b^k +\nabla u^{k+1} - d^{k+1}\\
            f^{k+1} &= f^k + f - F_u^k
        \end{aligned}
        \label{uk1min}
    \end{equation}
    Now is left to sole the minimization on the $u^{k+1}$ and $d^{k+1}$ operations.
    \textbf{Solution for u}\\
     The definition of $u^{k+1}$ in \ref{uk1min} is differentiable. We can hence get the minimum using the derivative. We the get:\\

\begin{equation}
	\begin{aligned}
		(\mu F^{T}F + \lambda \nabla^{T}\nabla) u^{k+1} = \mu F^{T}f^{k} + \lambda \nabla^{T}(d^{k}_x - b^{k}_x) 
	\end{aligned}
	\begin{aligned}
		K u^{k+1} = rhs^{k} 
	\end{aligned}
\end{equation}

\textbf{Solution for d}\\
    The expression of $d^{k+1}$ in \ref{uk1min} is not coiples. Hence the solution will be computed thanks to the shrinkage thresholding function:
    \begin{equation}
    	shrink(x,\gamma) = \frac{x}{|x|}\times max(|x| - \gamma, 0)
    \end{equation}
    so that:
    \begin{equation}
    	d^{k+1} =  shrink(\nabla u^{k+1} + b^k, 1/\lambda)
    \end{equation}
    
\section{SB-TV-3D}
    pbl: $\alpha ||(\nabla_x,\nabla_y, \nabla_z)u||_1 \mbox{such that} ||Fu - f||_2^2 < \delta^2$
    
    \begin{equation}
        \begin{aligned}
            u =\\
            d =
        \end{aligned}
    \end{equation}
    
    \section{Scalability}
    \begin{itemize}
    	\item ESRF -> Cluster, method, call projection, retro-projection explain what to change where in the algorithm
    \end{itemize}